---
title: "Retraining and exploration of the ToBaCCo MOFs"
author: "Ben Bucior"
date: "November 9, 2017"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(stringr)

library(purrr)
library(readxl)

library(caret)
library(glmnet)

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

theme_set(theme_bw(base_size=16) + theme(aspect.ratio=1))  # Default ggplot2 params
```

## Data import and processing

```{r load.data, include=FALSE}
h2_types <- paste0("h2.", c("g.L", "mol.kg", "wtp"))
tobacco_data <- read_xlsx(
  "BigData/CrystGrowthDesign_SI.xlsx",
  sheet = "data",
  skip = 3, na = "inf",
  col_names = c(
    "MOF.ID",
    "vf", "vsa", "gsa", "pld", "lcd",
    paste0(h2_types, ".100.77"),
    paste0(h2_types, ".100.130"),
    paste0(h2_types, ".100.200"),
    paste0(h2_types, ".100.243"),
    paste0("h2.qst.6.", c(77, 130, 200, 243)),
    paste0("ch4.", rep(c("v.v.", "mg.g."), 2), c("100.298", "100.298", "65.298", "65.298")),
    "ch4.qst.6.298",
    paste0("xe.kr.1.", c("xe", "kr", "select")),
    paste0("xe.kr.5.", c("xe", "kr", "select")),
    "topology",
    paste0("n1.", c("sym", "character", "ID")),
    paste0("n2.", c("sym", "character", "ID")),
    "cbb.ID"
    )
  )
tobacco_codes <- read_table2("BigData/mofs_map.dat", col_names = c("MOF.ID", "python.id"), col_types="ic")

tobacco_data <- tobacco_data %>% left_join(tobacco_codes, by="MOF.ID")

# Translate between Scotty's ID and the traditional ToBaCCo filename
scotty_codes <- read_tsv("BigData/tobacco-20171114/key.tsv", col_names = c("filename", "id"), col_types="cc")
scotty_codes <- scotty_codes %>% mutate(python.id = str_sub(filename, 1, -5))  # trim .cif suffix
tobacco_data <- tobacco_data %>% inner_join(scotty_codes, by="python.id")

DATA_SPLIT <- c(0.4, 0.4, 0.2)
R_GAS_KJ <- 8.314 / 1000
source("R/regression_and_features.R")  # Get regression utilities
```

```{r load_low_p}
# Also import the new low pressure data
low_p_h2_data <- read_tsv(
  "BigData/tobacco-20171114/clean-gcmc/comb-volume-77k.tsv",
  col_names = c("tob.num", "id", "h2.v.v.2.77", "h2.err.v.v.2.77"),  # TODO: verify that this is 2 bar, 77 K data for H2, and GCMC errors
  col_types = "icnn"
  )
low_p_h2_data <- low_p_h2_data %>% 
  mutate(`h2.g.L.2.77` = `h2.v.v.2.77` * 2.0 / 22.4) %>% 
  mutate(`h2.err.g.L.2.77` = `h2.err.v.v.2.77` * 2.0 / 22.4)
tobacco_data <- tobacco_data %>% inner_join(low_p_h2_data, by="id")  # For now, let's only import complete data
tobacco_data <- tobacco_data %>% mutate(h2.deliv.77 = h2.g.L.100.77 - h2.g.L.2.77)
```

```{r load_grids}
if (!exists("raw_grids_h2")) {
  raw_grids_h2 <- read_rds("BigData/Robj/tobacco_h2.Rds")
  # TODO: we should calculate the base histogram with less granularity (0.05 kJ/mol instead of 0.01) to considerably reduce file and processing size
}
```

```{r partition_data}
y_to_join <- tobacco_data %>% 
  rename(g.L = h2.deliv.77) %>% 
  select(id, g.L) %>% 
  filter(!(is.na(g.L) | g.L < 0))  # Clean up unphysical MOFs
complete_ids <- raw_grids_h2 %>% 
  select(id) %>% 
  unique() %>% 
  inner_join(y_to_join, by="id") %>% 
  select(id) %>% 
  unlist

y_to_join <- y_to_join %>% filter(id %in% complete_ids)
grids_h2 <- raw_grids_h2 %>% filter(id %in% complete_ids)

hist_sets <- partition_data_subsets(grids_h2, y_to_join, DATA_SPLIT)
```

Long-term, we also may consider moving this to a modular, independent R script to generate the figures all separately.  (Save models as R objects and import them individually as necessary, then ggsave the plots as their publication-ready formats)

## Proof-of-concept modeling
Let's run a quick ridge regression model on the ToBaCCo MOF set to see if the performance is similar to the hMOF results presented at AIChE.

Note: had to temporarily test with the hMOFs instead of ToBaCCo: the ToBaCCo MOFs lack sufficient diversity in volumetric uptake: they're considerably higher than the hMOFs, but also more tightly clustered which prevents the model from sufficiently generalizing.  Training on hMOFs and testing on ToBaCCo MOFs works great, unless we use some advanced sampling techniques on the ToBaCCo MOFs.

```{r model_proof_of_concept}
source("R/plot_hists.R")
source("R/regression_and_features.R")
source("R/get_energy_stats.R")

# TEMP BLOCK: test the hMOF results, overwriting ToBaCCo training/test:
source("R/load_data.R")
tob_hist_sets <- hist_sets
tob_y <- y_to_join
hmof_grid <- read_rds("BigData/Robj/hmof_h2.Rds")
hmof_grid <- hmof_grid %>%
  mutate(str_id = str_sub(id, 6, -1)) %>% # strip the hMOF- prefix
  mutate(id = as.integer(str_id)) %>% 
  select(-str_id)
y_to_join <- gcmc_data %>% 
  select(id, g.L) %>% 
  filter(!(is.na(g.L) | g.L < 0))
hist_sets <- partition_data_subsets(hmof_grid, y_to_join, DATA_SPLIT)
# Note: since we're starting with 2500 hMOFs, 40% for training is still 1000, so that works out great.



# Final saved results are ridge (alpha = 0)
for (perf_alpha in c(1, 0)) {
  hmof_partitioned_mod <- run_model_on_partitions(hist_sets, y_to_join, default_binspec, perf_alpha)
  print(hmof_partitioned_mod)
  trained_model <- hmof_partitioned_mod$trained_model
  trained_mod <- hmof_partitioned_mod$trained_mod
}
```


```{r tobacco_diagnostic}
# Try the hMOF model on the ToBaCCo data for sampling


# CRUDE ATTEMPT
# Let's use the above hMOF model on the ToBaCCo set.  How is the performance??
hist_sets <- tob_hist_sets
y_to_join <- tob_y
# First, how does its distribution of y values vary?  I think the model above is overfitting, given its mean capacity of 38 g/L
hist(y_to_join$g.L)

# COPIED FROM ABOVE: MAKE THIS A SUBROUTINE.
# MAYBE WE NEED A MODEL SETUP OBJECT, INCLUDING BINS AND OTHER PARAMS?
# Performance on the test data, which hasn't yet been used for anything
  testing_desc <- tob_hist_sets$testing %>% 
    stepped_hist(1.0, 1.0, -20, 1.0) %>% 
    spread(key=bin, value=metric)
  y_act <- testing_desc %>%
    left_join(tob_y, by="id") %>% 
    rename(y = g.L) %>% 
    .$y
  testing_ids <- testing_desc %>% select(id)
  testing_desc <- testing_desc %>% select(-id)
  
  y_pred <- pred_glmnet(trained_mod, testing_desc)
  postResample(pred=y_pred, obs=y_act) %>% print

  # NEW FOR COLORING
  has_hmof_topology <- testing_ids %>%
    select(id) %>% 
    left_join(tobacco_data, by="id")
  has_hmof_topology <- (has_hmof_topology$topology %in% c("pcu", "sra", "diab", "tbo", "nbo", "fcu"))

  p <- parity_plot(y_act, y_pred, ifelse(has_hmof_topology, "red", "gray"), 0.25)
  p <- p + ylab(paste0("Predicted uptake (", perf_model,")"))
  print(p)

  hist(y_act - y_pred)

  
  
# For diagnosis, we might consider plotting the various distributions to see how similar they are between the hMOFs and ToBaCCo MOFs
standardize(trained_mod, testing_desc) %>% .$`Inf` %>% hist

# Compare z/y/beta plots for the training hMOFs and test ToBaCCo MOFs
plot_bin_z_vs_y(trained_mod$x, trained_mod$y, coef_tbl(trained_mod$mod))
plot_bin_z_vs_y(standardize(trained_mod, testing_desc), y_act, coef_tbl(trained_mod$mod))
# What happens if we compare against the model instead of GCMC?  What does the "Inf" bin look like?
plot_bin_z_vs_y(standardize(trained_mod, testing_desc), y_pred, coef_tbl(trained_mod$mod))

# Finally, what are the distributions of z-scores (and actual values) between ToBaCCo and hMOFs?
x_distr <- function(x) {
  x %>% 
    gather(key="bin", value="value") %>% 
    ggplot(aes(value)) +
    geom_histogram() +
    facet_wrap(~bin, scales="free") +
    theme(text = element_text(size = 8))
}

x_distr(trained_mod$x)
x_distr(standardize(trained_mod, testing_desc))
# And the non-trainsformed versions
x_distr(select(trained_mod$orig_x, c("17", "18", "19", "20", "21", "Inf")))
x_distr(select(testing_desc, c("17", "18", "19", "20", "21", "Inf")))

```


