---
title: "Retraining and exploration of the ToBaCCo MOFs"
author: "Ben Bucior"
date: "November 9, 2017"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)

library(purrr)
library(readxl)

library(caret)
library(glmnet)

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

theme_set(theme_bw(base_size=16) + theme(aspect.ratio=1))  # Default ggplot2 params
```

```{r load.data, include=FALSE}
#source("R/load_data.R")
#source("R/get_energy_stats.R")
#hist_vals <- read_rds("BigData/init_h2_hist_vals.Rds")

h2_types <- paste0("h2.", c("g.L", "mol.kg", "wtp"))
tobacco_data <- read_xlsx(
  "BigData/CrystGrowthDesign_SI.xlsx",
  sheet = "data",
  skip = 3, na = "inf",
  col_names = c(
    "MOF.ID",
    "vf", "vsa", "gsa", "pld", "lcd",
    paste0(h2_types, ".100.77"),
    paste0(h2_types, ".100.130"),
    paste0(h2_types, ".100.200"),
    paste0(h2_types, ".100.243"),
    paste0("h2.qst.6.", c(77, 130, 200, 243)),
    paste0("ch4.", rep(c("v.v.", "mg.g."), 2), c("100.298", "100.298", "65.298", "65.298")),
    "ch4.qst.6.298",
    paste0("xe.kr.1.", c("xe", "kr", "select")),
    paste0("xe.kr.5.", c("xe", "kr", "select")),
    "topology",
    paste0("n1.", c("sym", "character", "ID")),
    paste0("n2.", c("sym", "character", "ID")),
    "cbb.ID"
    )
  )
tobacco_codes <- read_table2("BigData/mofs_map.dat", col_names = c("MOF.ID", "id"), col_types="ic")

tobacco_data <- tobacco_data %>% left_join(tobacco_codes, by="MOF.ID")

DATA_SPLIT <- c(0.4, 0.4, 0.2)
R_GAS_KJ <- 8.314 / 1000
source("R/regression_and_features.R")  # Get regression utilities
```


We need to get the energy grid results (and low pressure H2 calculations) before we can begin running any type of machine learning analysis.

Long-term, we also may consider moving this to a modular, independent R script to generate the figures all separately.  (Save models as R objects and import them individually as necessary, then ggsave the plots as their publication-ready formats)




